Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive PTSD diagnosis for GLAD/EDGI prepan
Added chunk to get positive no diagnosis for GLAD/EDGI prepan

>>>>

```{r Get PTSD positive for GLAD/EDGI}

GLAD.prepan_PTSD_positive <- GLAD.prepan %>%
  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)

GLAD.prepan_PTSD_positive <- GLAD.prepan_PTSD_positive %>% 
  summarise("PTSD" = n())

```{r Get control positive for GLAD/EDGI}

GLAD.prepan_control_positive <- GLAD.prepan %>%
  select(control_numeric) %>% 
  filter(control_numeric == 1)

GLAD.prepan_control_positive <- GLAD.prepan_control_positive %>% 
  summarise("No diagnosis" = n())
